Generalized Ensemble Spaces

### 2023-09-01 Notes/2023-GeneralizedEnsembleSpaces/GeneralizedEnsembleSpaces.tex
Added mention of the JS divervence

>>>>

\begin{remark}
	Note that $JSD(\rho_1, \rho_2 = )S(p_1\rho_1 + p_2 \rho_2) - (p_1 S(\rho_1) + p_2 S(\rho_2))$ is the Jensen Shannon divergence (\url{https://en.wikipedia.org/wiki/Jensen%E2%80%93Shannon_divergence}). The square root is a distance function, and therefore makes the convex space a metric space.
\end{remark}
